An improved metric for the analysis of swarms

### 2018-02-21 paper.tex
New Class

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{Images/NEGrey}}]{Neil Eliot}
is a Senior Lecturer at Northumbria University.  Neil was awarded his Ph.D. from Northumbria in 2017, his Pg.C. in 1994, and his B.Sc. in 1989 all in Computing. His research areas include swarm theory and cybersecurity. Neil is a Certified Ethical Hacker (CEH) and coordinator for the EC Council Academic alliance at Northumbria. He is also responsible for the delivery of several network cybersecurity modules in the area of operating systems integration, smart home technologies and modules that focus on cybersecurity threats in large scale system deployments. Prior to this Neil worked in the chemical industry and the NHS.
\end{IEEEbiography}

>>>>

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{Images/NEGrey}}]{Neil Eliot}
is a Senior Lecturer at Northumbria University.  Neil was awarded his Ph.D. from Northumbria in 2017, his Pg.C. in 1994, and his B.Sc. in 1989 all in Computing. His research areas include swarm theory and cybersecurity. Neil is a Certified Ethical Hacker (CEH) and coordinator for the EC Council Academic alliance at Northumbria. Prior to this Neil worked in the chemical industry and the NHS. His research interests are in the area of network cybersecurity, smart home technologies and swarm theory. 
\end{IEEEbiography}
